---
title: "WriteUp Linear Model with prediction"
author: "Onalee Garusinghe"
date: "2024-10-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)

data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

## Model1: SIMS~ARM

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

  This scatter plot has a positive slope going up. This shows the average amount of strength lies withing 50 and 100. What the plot describes is the relation of arm strength for the select employees.

### Numerical Results

```{r}
cor(SIMS~ARM,data=data)
```

This has a high positive correlation for SIMS~ARM. The closer to 1, the results get a higher correlation. Because of this, we can say that they are related to each other.

### Inferential Results
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

From the inferential results, we can get our equation for our line of best fit. > SIMS = 0.054563 * ARM - 4.095160.

### Create target

```{r}
target<-data.frame(ARM=90, GRIP=90)
```

### Predict Target Point of Model 1

```{r}
predict(model.1,target,interval=c("prediction"))
```
  Our plots prediction is 0.8155096. According to the prediction the values will be between -1.617843 and 3.248863.
  
### Linear Fit Model1

```{r}
basicNN + geom_point() + ggtitle("SIMS~ARM")+ theme(plot.title = element_text(hjust = 0.5, size = 20))+ geom_smooth(method=lm)
```

### Model2: SIMS~GRIP

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basicNN + geom_point() + ggtitle("SIMS~GRIP")+ theme(plot.title = element_text(hjust = 0.5, size = 20))
```

The scatter plot shows a positive slope going upright. This is a visual correlation between SIMS~GRIP.

### Numerical Results

```{r}
cor(SIMS~GRIP,data=data)
```

The correlation value is close to 1 which is positive. This shows a high correlation.

### Inferential Results
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

Our estimated equation for model2 is SIMS = 0.045463GRIP -4.809675 for our line of best fit.

### Predict Target Point of Model 2

```{r}
predict(model.1,target,interval=c("prediction"))
predict(model.2,target,interval=c("prediction"))
```
Model2 is predicted to be -0.7180063. The prediction values will be between -3.292089 and 1.856077.

### Linear Fit Model2

```{r}
basicNN + geom_point() + ggtitle("SIMS~GRIP")+ theme(plot.title = element_text(hjust = 0.5, size = 20))+ geom_smooth(method=lm)
```

### Model3: SIMS~ARM+GRIP

### Numerical Results

```{r}
cor(SIMS~ARM,data=data)
cor(SIMS~GRIP,data=data)
cor(SIMS~ARM+GRIP,data=data)
```
The value is higher than the other 2 models. Model 3 has a very high positive correlation.

### Inferential Results
  
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

Our equation is SIMS = 0.037311ARM + 0.024470GRIP + -5.433871. This is our estimated 3D line. 

### Predict Target Point of Model 3

```{r}
predict(model.1,target,interval=c("prediction"))
predict(model.2,target,interval=c("prediction"))
predict(model.3,target,interval=c("prediction"))
```

The predicted model shows 0.1263886. The predicted values be between -2.1626 and 2.415377

### Anova Tests for Models

### Model1~Model3

```{r}
anova(model.1,model.3)
```

Our p-value is 0.000004994 which is very small. Our difference is 29. Model 1 had all errors add up to 217.88. Model 3's errors added up to 188.43. This shows that model 3 is better than model 1, a significant difference.

### Model2~Model3

```{r}
anova(model.2,model.3)
```

Our p-value is 0.000000001495. Models 2's errors add up to 243.07. This models is also smaller than model 3 and less accurate, another significant difference. Our difference is 54.639. Model 3 is still the most accurate model of the 2 models. 

### Model1~Model2

```{r}
anova(model.1,model.2)
```

The sum of squared errors of model 1 has less errors than model 2. The difference of the 2 models is -25.189.

### Discussion and Conclusion

First I imported the data from the given website. I then manipulated the data into 3 different models. Model 1 is SIMS~ARM, model 2 is SIMS~GRIP, model 3 is SIMS~ARM+GRIP. We used prediction code blocks to visualize the estimated values alongside scatter plots to see the line of best fit. We then used anova at the end to compare all 3 models. The analysis showed that model 3 had the best accuracy out of all 3.



